01 - Simulate data

### 2023-12-09 scripts/01_sim_data.qmd

We simulate data of the U-shaped effect of language acquisition. Subjects take a test at 11 time points where they language proficiency is measured and a score value is obtained for how well they have learnt construction C.

@@

dat2 <- dat2 %>%
  mutate(
    id = paste(group, subj, rep, sep = ".")
  )

>>>>

We simulate data of the U-shaped effect of language acquisition. Subjects take a test at 11 time points where their language proficiency is measured and a score value is obtained for how well they have learnt construction C.

@@

dat2 <- dat2 %>%
  mutate(
    id = paste(group, subj, rep, sep = "."),
    subj = as.factor(paste(group, subj, sep = "_"))
  )
